Understanding meta-analysis through data simulation with applications to power analysis

### 2023-09-27 documents/output/paper.tex
fixing formula

\NormalTok{v }\OtherTok{\textless{}{-}}\NormalTok{ (n }\SpecialCharTok{+}\NormalTok{ n)}\SpecialCharTok{/}\NormalTok{(n }\SpecialCharTok{*}\NormalTok{ n) }\SpecialCharTok{+}\NormalTok{ mu\_theta}\SpecialCharTok{\^{}}\DecValTok{2}\SpecialCharTok{/}\NormalTok{(}\DecValTok{2} \SpecialCharTok{*}\NormalTok{ (n }\SpecialCharTok{+}\NormalTok{ n }\SpecialCharTok{{-}} \DecValTok{2}\NormalTok{)) }\CommentTok{\# typical within study variance}
\NormalTok{tau2 }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\NormalTok{((I2}\SpecialCharTok{*}\NormalTok{v)}\SpecialCharTok{/}\NormalTok{(I2 }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{))}

@@

\caption{\label{tab:res-random-effects-i2}Summary of the random-effects model fixing the \(I^2\) value. Parameters are the same as described in Table \ref{tab:res-random-effects}.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.305 (SE = 0.072) & $[0.164, 0.447]$ & 4.226 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2 = 0.091$ ($SE = 0.041$)}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 58.479\%$}\\
\end{tabular}
\end{table}

>>>>

\NormalTok{v }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{/}\NormalTok{n }\SpecialCharTok{+} \DecValTok{1}\SpecialCharTok{/}\NormalTok{n }\CommentTok{\# typical within study variance}
\NormalTok{tau2 }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\NormalTok{((I2}\SpecialCharTok{*}\NormalTok{v)}\SpecialCharTok{/}\NormalTok{(I2 }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{))}

@@

\caption{\label{tab:res-random-effects-i2}Summary of the random-effects model fixing the \(I^2\) value. Parameters are the same as described in Table \ref{tab:res-random-effects}.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.305 (SE = 0.072) & $[0.164, 0.447]$ & 4.239 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2 = 0.090$ ($SE = 0.041$)}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 58.183\%$}\\
\end{tabular}
\end{table}
